A Switching Planner for Combined Task and Observation Planning

### 2011-02-04 subarchitectures/planner.sa/trunk/src/latex/AAAI11/dtpddl.tex
small change

\noindent Where the first symbol models the actual location of
objects, and the second symbol the instantaneous sensing of objects
following application of an action with sensing consequences.
%%
To model sensing capabilities, we have operator-like declarations,
with preconditions expressed using state and action symbols, and
uniformly positive effects over perceptual symbols. For example, where
{\em look-for-object} is the operator that applies an object detection
algorithm at a specific place, in a simplified {\em object search} task
we have:

>>>>

\noindent Where the first fluent symbol models the actual location of
objects, and the second the instantaneous sensing of objects
following application of an action with sensing consequences.
%%
To model sensing capabilities, we have operator-like declarations,
with preconditions expressed using state and action symbols, and
uniformly positive effects over perceptual symbols. For example, where
{\em look-for-object} is the operator that applies an object detection
algorithm at a specific place, in a simplified {\em object search} task
we have:
